Holomorphic field theories and higher algebra

### 2024-09-18 draft.tex
chiral sectors question
tidying up small things

In physics, a classical field theory is usually described in terms of a few pieces of data:
\begin{itemize}
\item a manifold $M$ that plays the role of ``spacetime,''
\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
\item a system of PDE for the fields, known as the equations of motion.
\end{itemize}
These equations of motion are variational: 
they are the Euler-Lagrange equations of an action functional on the space a fields.
An action functional is written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
A few examples will illuminate this sketch.

@@

>>>>

In physics, a classical field theory is usually described in terms of a few pieces of data:
\begin{itemize}
\item a manifold $M$ that plays the role of ``spacetime,''
\item a space of fields, such as sections of some fiber bundle $F \to M$ or connections on a principal bundle on $M$, and
\item a system of PDE for the fields, known as the equations of motion.
\end{itemize}
These equations of motion are variational: 
they are the Euler-Lagrange equations of an action functional on the space of fields,
so that solutions to these PDE are the critical points, in a sense, of some function.
In practice an action functional is a formal expression, 
written as an integral over $M$ of some polydifferential operator on the fields that takes values in densities of~$M$.
A few examples will illuminate this sketch.

@@

\owen{I'm a little lost about the motivation for this section, 
given the earlier scalar field section. This C theory looks interest so maybe we can figure out a natural place to put it?}
